---
title: "Analyze AEA Survey with Weights"
author-title: "Authors"
authors: "Aaron R. Williams and Joshua Snoke"
affiliation: "Urban Institute and RAND Corp."
date: today
format:
  html:
    theme: www/urbn.scss
    self-contained: true
    code-fold: true
    code-line-numbers: true
    html-math-method: katex
    df-print: paged
    toc: true
    toc-depth: 3
    number-sections: true
    number-depth: 3
    highlight-style: pygments
#bibliography: references.bib
execute: 
  warning: false
  message: false
  fig-width: 6.5
  fig-hieght: 4
editor_options: 
  chunk_output_type: console
---

# Stock Analysis

```{r}
library(freqtables)
library(quantreg)
library(here)
library(srvyr)
library(tidyverse)
library(urbnthemes)
library(scales)

source(here('R', 'make_analysis_data.R'))

options(scipen = 999)

set_urbn_defaults(style = "print")

```

```{r opts, echo = FALSE}
knitr::opts_chunk$set(
  fig.path = "../figures/"
)
```


```{r results = "hide"}
aea_analysis_weighted <- read_csv(here("data", "aea_analysis_weighted.csv"))

aea_weighted <- aea_analysis_weighted %>%
  as_survey(weights = final_weights)

```

## Section 1

We drop missing values after calculating proportions for these questions. Starting in section 2, we drop missing values before calculating proportions. 

### Question 1

1.1: Do you reside in the United States?

```{r q1.1}
aea_weighted %>%
  group_by(Q1_1) %>%
  summarize(survey_prop(vartype = "ci")) %>%
  mutate(Q1_1 = factor(Q1_1, levels = c("Yes", "No"))) %>%
  ggplot(aes(Q1_1, coef)) +
  geom_col() +
  scale_y_continuous(
    labels = scales::percent,
    expand = expansion(mult = c(0, 0.2))
  ) +
  labs(
    title = "Do you reside in the United States?",
    x = NULL,
    y = NULL
  ) +
  remove_ticks()

```

```{r}
aea_weighted %>%
  group_by(Q1_1) %>%
  summarize(survey_prop(vartype = "ci"))

```

1.2: Are you currently a student?

```{r q1.2}
aea_weighted %>%
  group_by(Q1_2) %>%
  summarize(n(), survey_prop(vartype = "ci")) %>%
  filter(!is.na(Q1_2)) %>%
  mutate(Q1_2 = factor(Q1_2, levels = c("Yes", "No"))) %>%
  ggplot(aes(Q1_2, coef)) +
  geom_col() +
  scale_y_continuous(
    labels = scales::percent,
    expand = expansion(mult = c(0, 0.2))
  ) +
  labs(
    title = "Are You Currently a Student?",
    x = NULL,
    y = NULL
  ) +
  remove_ticks()

```


```{r}
aea_weighted %>%
  group_by(Q1_2) %>%
  summarize(n(), survey_prop(vartype = "ci"))

```

1.3: What is the highest degree or level of school you have completed?

```{r q1.3}
aea_weighted %>%
  group_by(Q1_3) %>%
  summarize(n(), survey_prop(vartype = "ci")) %>%
  slice(1:5) %>%
  mutate(Q1_3 = fct_recode(
    Q1_3, 
    `High school or General\nEducational Development (GED)` = 
      "High school or General Educational Development (GED)")
  ) %>%  
  ggplot(aes(coef, Q1_3)) +
  geom_col() +
  scale_x_continuous(
    labels = scales::percent,
    expand = expansion(mult = c(0, 0.2))
  ) +
  labs(
    title = "What is the highest degree or level of school you have completed?",
    x = NULL,
    y = NULL
  ) +
  theme(panel.grid = element_blank())

```

```{r}
aea_weighted %>%
  group_by(Q1_3) %>%
  summarize(n(), survey_prop(vartype = "ci"))

```

1.4: In what year did you finish your highest degree or level of school?

```{r q1.4}
missing_q1.4 <- sum(is.na(pull(aea_weighted, Q1_4)))

aea_weighted %>%
  group_by(Q1_4) %>%
  summarize(n(), survey_prop(vartype = "ci")) %>%
  filter(!is.na(Q1_4)) %>%
  mutate(Q1_4 = factor(Q1_4, levels = c("Early-Career", "Mid-Career", "Late-Career"))) %>%
  ggplot(aes(Q1_4, coef)) +
  geom_col() +
  scale_y_continuous(
    labels = scales::percent,
    expand = expansion(mult = c(0, 0.2))
  ) +
  labs(
    title = "In what year did you finish your highest degree or level of school?",
    x = NULL,
    y = NULL,
    caption = paste(missing_q1.4, "respondents did not answer")
  )

```

1.5: Which of the following best describes your most recent primary employer?

```{r q1.5}
missing_q1.5 <- sum(is.na(pull(aea_weighted, Q1_5)))

aea_weighted %>%
  group_by(Q1_5) %>%
  summarize(n(), survey_prop(vartype = "ci")) %>%
  filter(!is.na(Q1_5)) %>%
  ggplot(aes(coef, Q1_5)) +
  geom_col() +
  scale_x_continuous(
    labels = scales::percent,
    expand = expansion(mult = c(0, 0.2))
  ) +
  labs(
    title = "Which of the following best describes your most recent primary employer?",
    x = NULL,
    y = NULL,
    caption = paste(missing_q1.5, "respondents did not answer")
  ) +
  theme(panel.grid = element_blank())

```

```{r}
aea_weighted %>%
  group_by(Q1_5) %>%
  summarize(n(), survey_prop(vartype = "ci"))

```

1.6: Have you refereed at least one peer-reviewed journal article in the past five years?

```{r q1.6}
missing_q1.6 <- sum(is.na(pull(aea_weighted, Q1_6)))

aea_weighted %>%
  group_by(Q1_6) %>%
  summarize(n(), survey_prop(vartype = "ci")) %>%
  filter(!is.na(Q1_6)) %>%
  ggplot(aes(Q1_6, coef)) +
  geom_col() +
  scale_y_continuous(
    labels = scales::percent,
    expand = expansion(mult = c(0, 0.2))
  ) +
  labs(
    title = "Have you refereed at least one peer-reviewed journal article in the past five years?",
    x = NULL,
    y = NULL,
    caption = paste(missing_q1.6, "respondents did not answer")
  ) +
  remove_ticks()

```

```{r}
aea_weighted %>%
  group_by(Q1_6) %>%
  summarize(n(), survey_prop(vartype = "ci"))

```

## Section 2

Starting in section 2, we drop missing values before calculating proportions. 

### Question 1 {.tabset}

Q2_1 - 2.1: Please rate the following methods based on how frequently you have used the method on cross-sectional data in the past year:

#### Visualization

```{r q2.1}
responses <- c("Always", "Frequently")

aea_weighted %>%
  summarize(
    `Multiple linear regression` = survey_mean(Q2_1_1 %in% responses, na.rm = TRUE),
    `Weighted multiple linear regression` = survey_mean(Q2_1_2 %in% responses, na.rm = TRUE),
    `Tobit` = survey_mean(Q2_1_3 %in% responses, na.rm = TRUE),
    `Probit/logit regression` = survey_mean(Q2_1_4 %in% responses, na.rm = TRUE),
    `Regression discontinuity or kink design` = survey_mean(Q2_1_5 %in% responses, na.rm = TRUE),
    `Merging multiple data sources` = survey_mean(Q2_1_6 %in% responses, na.rm = TRUE),
    `Two Stage Least Squares (2SLS)` = survey_mean(Q2_1_7 %in% responses, na.rm = TRUE)
  ) %>%
  select(!ends_with("_se")) %>%
  pivot_longer(
    everything(),
    names_to = "Method", 
    values_to = "Proportion 'Always' or 'Frequently'"
  ) %>%
  mutate(Method = fct_reorder(Method, `Proportion 'Always' or 'Frequently'`)) %>%
  ggplot(aes(x = `Proportion 'Always' or 'Frequently'`, y = Method)) +
  geom_col() +
  geom_text(aes(label = label_percent(accuracy = 0.1)(`Proportion 'Always' or 'Frequently'`), hjust = -0.3)) +
  scale_x_continuous(
    labels = scales::percent,
    limits = c(0, 0.8)
  ) +
  labs(
    title = "Multiple Linear Regression Is the Most Popular Method",
    subtitle = 'Percentage of Respondents Rating Each Method with "Always" or "Frequently"',
    x = NULL,
    y = NULL,
    caption = "147 respondents did not answer"
  ) +
  theme(panel.grid = element_blank())

```

#### Table

```{r}
survey_count(aea_weighted, missing_all = is.na(Q2_1_1) & is.na(Q2_1_2) & is.na(Q2_1_3) & is.na(Q2_1_4) & is.na(Q2_1_5) & is.na(Q2_1_6) & is.na(Q2_1_7))

```

Multiple linear regression

```{r}
survey_count(aea_weighted, Q2_1_1)

```

Weighted multiple linear regression

```{r}
survey_count(aea_weighted, Q2_1_2)

```

Tobit

```{r}
survey_count(aea_weighted, Q2_1_3)

```

Probit/logit regression

```{r}
survey_count(aea_weighted, Q2_1_4)

```

Regression discontinuity or kink design

```{r}
survey_count(aea_weighted, Q2_1_5)

```

Merging multiple data sources

```{r}
survey_count(aea_weighted, Q2_1_6)

```

Two Stage Least Squares (2SLS)

```{r}
survey_count(aea_weighted, Q2_1_7)

```

### Question 2

See analysis-text.qmd.

### Question 3 {.tabset}

2.3: Please rate the following information obtained from multiple linear regression based on its importance for your work:

#### Visualization

```{r q2.3}
responses <- c("Very important", "Important")

aea_weighted %>%
  summarize(
    `Estimated coefficients` = survey_mean(Q2_3_1 %in% responses, na.rm = TRUE),
    `Estimated standard errors, T-statistics for\ncoefficients, or P-values for coefficients` = mean(Q2_3_2 %in% responses, na.rm = TRUE),
    `Adjusted or multiple R-Squared of\nthe regression line` = survey_mean(Q2_3_3 %in% responses, na.rm = TRUE),
    `F-statistic on the regression` = survey_mean(Q2_3_4 %in% responses, na.rm = TRUE),
    `Residuals` = mean(Q2_3_5 %in% responses, na.rm = TRUE),
    `Residual standard error` = survey_mean(Q2_3_6 %in% responses, na.rm = TRUE),
    `Predicted values` = survey_mean(Q2_3_7 %in% responses, na.rm = TRUE),
    `Average predicted values for a given\ncharacteristic or marginal predictions` = survey_mean(Q2_3_8 %in% responses, na.rm = TRUE)
  ) %>%
  select(!ends_with("_se")) %>%
  pivot_longer(
    everything(),
    names_to = "Method", 
    values_to = "Proportion 'Very important' or 'Important'"
  ) %>%
  mutate(Method = fct_reorder(Method, `Proportion 'Very important' or 'Important'`)) %>%
  ggplot(aes(x = `Proportion 'Very important' or 'Important'`, y = Method)) +
  geom_col() +
  geom_text(aes(label = label_percent(accuracy = 0.1)(`Proportion 'Very important' or 'Important'`), hjust = -0.3)) +  
  scale_x_continuous(
    labels = scales::percent,
    limits = c(0, 0.82)
  ) +
  labs(
    title = "Coefficient-Level Information Is the Most Important",
    subtitle = 'Proportion of Respondents Rating Each Component with "Very important" or "Important"',
    x = NULL,
    y = NULL,
    caption = "170 respondents did not answer"
  ) +
  theme(panel.grid = element_blank())

```

#### Table

```{r}
survey_count(aea_weighted, missing_all = is.na(Q2_3_1) & is.na(Q2_3_2) & is.na(Q2_3_3) & is.na(Q2_3_4) & is.na(Q2_3_5) & is.na(Q2_3_6) & is.na(Q2_3_7) & is.na(Q2_3_8))

```

Estimated coefficients

```{r}
survey_count(aea_weighted, Q2_3_1)

```

Estimated standard errors, T-statistics for coefficients, or P-values for coefficients

```{r}
survey_count(aea_weighted, Q2_3_2)

```

Adjusted or multiple R-Squared of the regression line

```{r}
survey_count(aea_weighted, Q2_3_3)

```

F-statistic on the regression

```{r}
survey_count(aea_weighted, Q2_3_4)

```

Residuals

```{r}
survey_count(aea_weighted, Q2_3_5)

```

Residual standard error

```{r}
survey_count(aea_weighted, Q2_3_6)

```

Predicted values

```{r}
survey_count(aea_weighted, Q2_3_7)

```

Average predicted values for a given characteristic or marginal predictions

```{r}
survey_count(aea_weighted, Q2_3_8)

```

### Question 5

See analysis-text.qmd.

## Section 3

### Question 1

Q3_1 - 3.1: Please rate your familiarity with the concept of differential privacy.

```{r q3.1}
missing_q3.1 <- sum(is.na(pull(aea_weighted, Q3_1)))

aea_weighted %>%
  filter(!is.na(Q3_1)) %>%
  group_by(Q3_1) %>%
  summarize(n(), survey_prop(vartype = "ci")) %>%
  mutate(Q3_1 = fct_recode(
    Q3_1, 
    `Have heard the term but am\nnot familiar with any details` = 
      "Have heard the term but am not familiar with any details",
    `Have read a blog, newspaper, or non-academic\nreport or discussion on the topic` = 
      "Have read a blog, newspaper, or non-academic report or discussion on the topic",
    `Feel confident implementing\nthese methods on my own` = 
      "Feel confident implementing these methods on my own")
  ) %>%
  mutate(Q3_1 = fct_rev(Q3_1)) %>%
  ggplot(aes(coef, Q3_1)) +
  geom_col() +
  geom_text(aes(label = label_percent(accuracy = 0.1)(coef), hjust = -0.1)) +
  scale_x_continuous(
    labels = scales::percent,
    expand = expansion(mult = c(0, 0.2))
  ) + 
  labs(
    title = "Most Respondents Knew Nothing about Differential Privacy",
    subtitle = "Text: Please rate your familiarity with the concept of differential privacy",
    x = NULL,
    y = NULL,
    caption = paste(missing_q3.1, "respondents did not answer")
  ) +
  theme(panel.grid = element_blank())

aea_weighted %>%
  filter(!is.na(Q3_1)) %>%
  group_by(Q3_1) %>%
  summarize(n(), survey_prop(vartype = "ci"))

```

```{r q3.1-primary-employer, fig.width=10}
missing_q3.1_employer <- sum(is.na(pull(aea_weighted, Q3_1)) | is.na(pull(aea_weighted, Q1_5)))

aea_weighted %>%
  filter(
    !is.na(as.character(Q3_1)),
    !is.na(as.character(Q1_5))
  ) %>%  
  mutate(
    Q1_5 = fct_recode(
      Q1_5,
      `Industry (For or Not-for profit)` = "For-profit business",
      `Industry (For or Not-for profit)` = "Not-for-profit",
      `Government` = "Federal government",
      `Government` = "State or local government"
    )
  ) %>%
  group_by(Q3_1, Q1_5) %>%
  summarize(n(), survey_prop(vartype = "ci")) %>%
  ungroup() %>%
  mutate(Q3_1 = fct_recode(
    Q3_1, 
    `Have heard the term but am\nnot familiar with any details` = 
      "Have heard the term but am not familiar with any details",
    `Have read a blog, newspaper, or non-academic\nreport or discussion on the topic` = 
      "Have read a blog, newspaper, or non-academic report or discussion on the topic",
    `Feel confident implementing\nthese methods on my own` = 
      "Feel confident implementing these methods on my own")
  ) %>%
  mutate(Q3_1 = fct_rev(Q3_1)) %>%
  ggplot(aes(coef, Q3_1)) +
  geom_col() +
  geom_text(aes(label = label_percent(accuracy = 0.1)(coef), hjust = -0.2)) + 
  scale_x_continuous(
    labels = scales::percent,
    expand = expansion(mult = c(0, 0.2))
  ) + 
  facet_wrap(~Q1_5, scales = "free_x") +
  labs(
    title = "Most Respondents Knew Nothing about Differential Privacy",
    subtitle = "Text: Please rate your familiarity with the concept of differential privacy",
    x = NULL,
    y = NULL,
    caption = paste(missing_q3.1_employer, "respondents did not answer")
  ) +
  theme(
    panel.grid = element_blank(),
    panel.spacing = unit(2, "lines")
  )

```

```{r}
aea_weighted %>%
  filter(
    !is.na(as.character(Q3_1)),
    !is.na(as.character(Q1_5))
  ) %>%  
  mutate(
    Q1_5 = fct_recode(
      Q1_5,
      `Industry (For or Not-for profit)` = "For-profit business",
      `Industry (For or Not-for profit)` = "Not-for-profit",
      `Government` = "Federal government",
      `Government` = "State or local government"
    )
  ) %>%
  group_by(Q3_1, Q1_5) %>%
  summarize(n(), survey_prop(vartype = "ci")) %>%
  ungroup()

```

### Question 2

Q3_2 - 3.2: Please rate your familiarity with the concept of formal privacy

```{r q3.2}
missing_q3.2 <- sum(is.na(pull(aea_weighted, Q3_2)))

aea_weighted %>%
  filter(!is.na(Q3_2)) %>%
  group_by(Q3_2) %>%
  summarize(n(), survey_prop(vartype = "ci")) %>%
  mutate(Q3_2 = fct_recode(
    Q3_2,
    `Have heard the term in relation to Differential\nPrivacy, but I do not know the difference` =
      "Have heard the term in relation to Differential Privacy, but I do not know the difference",
    `Am familiar with the concept and the distinction\nfrom differential privacy` = 
      "Am familiar with the concept and the distinction from differential privacy")
  ) %>%
  mutate(Q3_2 = fct_rev(Q3_2)) %>%
  ggplot(aes(coef, Q3_2)) +
  geom_col() +
  geom_text(aes(label = label_percent(accuracy = 0.01)(coef), hjust = -0.2)) +
  scale_x_continuous(
    labels = scales::percent,
    expand = expansion(mult = c(0, 0.2))
  ) + 
  labs(
    title = "Most Respondents Knew Nothing about Formal Privacy",
    subtitle = "Text: Please rate your familiarity with the concept of formal privacy",
    x = NULL,
    y = NULL,
    caption = paste(missing_q3.2, "respondents did not answer")
  ) +
  theme(panel.grid = element_blank())

```

```{r}
aea_weighted %>%
  filter(!is.na(Q3_2)) %>%  
  group_by(Q3_2) %>%
  summarize(n(), survey_prop(vartype = "ci"))

```

### Question 3

Q3_3 - 3.3: What share of economists you know in your professional circles have discussed the US Census Bureau's adoption of differential privacy/formal privacy for the 2020 Census?

```{r q3.3}
missing_q3.3 <- sum(is.na(pull(aea_weighted, Q3_3)))

aea_weighted %>%
  filter(!is.na(Q3_3)) %>%  
  group_by(Q3_3) %>%
  summarize(n(), survey_prop(vartype = "ci")) %>%
  mutate(Q3_3 = fct_rev(Q3_3)) %>%
  ggplot(aes(coef, Q3_3)) +
  geom_col() +
  geom_text(aes(label = label_percent(accuracy = 0.01)(coef), hjust = -0.2)) +
  scale_x_continuous(
    labels = scales::percent,
    expand = expansion(mult = c(0, 0.2))
  ) + 
  labs(
    title = "Most Economists Have Not Discussed Differential Privacy and the 2020 Census",
    subtitle = "Text: What share of economists you know in your professional circles have discussed the US Census Bureau's\nadoption of differential privacy/formal privacy for the 2020 Census?",
    x = NULL,
    y = NULL,
    caption = paste(missing_q3.3, "respondents did not answer")
  ) +
  theme(panel.grid = element_blank())

```

### Question 4

Q3_4 - 3.4: What share of economists you know in your professional circles work with differential privacy/formal privacy methods?

```{r q3.4}
missing_q3.4 <- sum(is.na(pull(aea_weighted, Q3_4)))

aea_weighted %>%
  filter(!is.na(Q3_4)) %>%  
  group_by(Q3_4) %>%
  summarize(n(), survey_prop(vartype = "ci")) %>%
  mutate(Q3_4 = fct_rev(Q3_4)) %>%
  ggplot(aes(coef, Q3_4)) +
  geom_col() +
  geom_text(aes(label = label_percent(accuracy = 0.01)(coef), hjust = -0.2)) +
  scale_x_continuous(
    labels = scales::percent,
    expand = expansion(mult = c(0, 0.2))
  ) + 
  labs(
    title = "Most Economists Don't Work with Differential Privacy",
    subtitle = "Text: What share of economists you know in your professional circles work with differential privacy/formal\nprivacy methods?",
    x = NULL,
    y = NULL,
    caption = paste(missing_q3.4, "respondents did not answer")
  ) +
  theme(panel.grid = element_blank())

```

### Question 5

Q3_5 - 3.5: I do not have an opinion on Differential Privacy/formal privacy

```{r q3.5}
missing_q3.5 <- sum(is.na(pull(aea_weighted, Q3_5)))

aea_weighted %>%
  filter(!is.na(Q3_5)) %>%  
  group_by(Q3_5) %>%
  summarize(n(), survey_prop(vartype = "ci")) %>%
  mutate(Q3_5 = fct_rev(Q3_5)) %>%
  ggplot(aes(coef, Q3_5)) +
  geom_col() +
  geom_text(aes(label = label_percent(accuracy = 0.1)(coef), hjust = -0.2)) + 
  scale_x_continuous(
    labels = scales::percent,
    expand = expansion(mult = c(0, 0.2))
  ) +   
  labs(
    title = "Most Respondents Have no Opinion on Differential Privacy",
    subtitle = "Text: I do not have an opinion on Differential Privacy/formal privacy",
    x = NULL,
    y = NULL,
    caption = paste(missing_q3.5, "respondents did not answer")
  ) +
  theme(panel.grid = element_blank())

```

```{r}
aea_weighted %>%
  filter(!is.na(Q3_5)) %>%   
  group_by(Q3_5) %>%
  summarize(n(), survey_prop(vartype = "ci")) 

```

### Question 6

Q3_6 - Differential privacy/formal privacy is a new approach to protecting privacy that seems to be mostly popular among computer scientists.

```{r q3.6}
missing_q3.6 <- sum(is.na(pull(aea_weighted, Q3_6)))

aea_weighted %>%
  filter(!is.na(Q3_6)) %>%  
  group_by(Q3_6) %>%
  summarize(n(), survey_prop(vartype = "ci")) %>%
  mutate(Q3_6 = fct_rev(Q3_6)) %>%
  ggplot(aes(coef, Q3_6)) +
  geom_col() +
  geom_text(aes(label = label_percent(accuracy = 0.1)(coef), hjust = -0.2)) +  
  scale_x_continuous(
    labels = scales::percent,
    expand = expansion(mult = c(0, 0.2))
  ) +   
  labs(
    title = "Most Economists think Differential Privacy is Popular with Computer Scientists",
    subtitle = "Text: Differential privacy/formal privacy is a new approach to protecting privacy that seems to be mostly popular\namong computer scientists.",
    x = NULL,
    y = NULL,
    caption = paste(missing_q3.6, "respondents did not answer")
  ) +
  theme(panel.grid = element_blank())

```

### Question 7

Q3_7 - Differential privacy/formal privacy is an approach to protecting privacy that distorts the results more than necessary given the actual risks.

```{r q3.7}
missing_q3.7 <- sum(is.na(pull(aea_weighted, Q3_7)))

aea_weighted %>%
  filter(!is.na(Q3_7)) %>%  
  group_by(Q3_7) %>%
  summarize(n(), survey_prop(vartype = "ci")) %>%
  mutate(Q3_7 = fct_rev(Q3_7)) %>%
  ggplot(aes(coef, Q3_7)) +
  geom_col() +
  geom_text(aes(label = label_percent(accuracy = 0.1)(coef), hjust = -0.2)) +  
  scale_x_continuous(
    labels = scales::percent,
    expand = expansion(mult = c(0, 0.2))
  ) +   
  labs(
    title = "Economists with Opinions About Differential Privacy Appear Skeptical of\nDifferential Privacy",
    subtitle = "Text: Differential privacy/formal privacy is an approach to protecting privacy that distorts the results more than\nnecessary given the actual risks",
    x = NULL,
    y = NULL,
    caption = paste(missing_q3.7, "respondents did not answer")
  ) +
  theme(panel.grid = element_blank())

```

### Question 8

Q3_8 - Differential privacy/formal privacy is a needed approach to preserve privacy in the face of expanding disclosure risks that current methods are unable to address.

```{r q3.8}
missing_q3.8 <- sum(is.na(pull(aea_weighted, Q3_8)))

aea_weighted %>%
  filter(!is.na(Q3_8)) %>%  
  group_by(Q3_8) %>%
  summarize(n(), survey_prop(vartype = "ci")) %>%
  mutate(Q3_8 = fct_rev(Q3_8)) %>%
  ggplot(aes(coef, Q3_8)) +
  geom_col() +
  geom_text(aes(label = label_percent(accuracy = 0.1)(coef), hjust = -0.2)) + 
  scale_x_continuous(
    labels = scales::percent,
    expand = expansion(mult = c(0, 0.2))
  ) +   
  labs(
    title = "Economists with Opinions About Differential Privacy Appear Skeptical of\nDifferential Privacy",
    subtitle = "Text: Differential privacy/formal privacy is a needed approach to preserve privacy in the face of expanding\ndisclosure risks that current methods are unable to address",
    x = NULL,
    y = NULL,
    caption = paste(missing_q3.8, "respondents did not answer")
  ) +
  theme(panel.grid = element_blank())

```

## Section 4

### Question 1

What is the largest percentage of significance mismatch you would accept before...?

```{r}
aea_weighted %>%
  group_by(is.na(Q4_1_1)) %>%
  summarize(n())

aea_weighted %>%
  group_by(is.na(Q4_1_2)) %>%
  summarize(n())

probs <- c(0, 0.05, 0.25, 0.5, 0.75, 0.95, 1)

aea_weighted %>%
  summarize(
    sig_mismatch = survey_quantile(Q4_1_1, quantiles = probs, na.rm = TRUE)
  )

aea_weighted %>%
  summarize(
    sig_mismatch = survey_quantile(Q4_1_2, quantiles = probs, na.rm = TRUE)
  )

```

```{r q4.1}
missing_q4.1 <- sum(is.na(pull(aea_weighted, Q4_1_1)) | is.na(pull(aea_weighted, Q4_1_2)))

ggplot() +
  geom_point(
    data = aea_weighted$variables,
    mapping = aes(Q4_1_1 / 100, Q4_1_2 / 100), 
    alpha = 0.05
  ) +
  geom_point(
    data = summarize(aea_weighted, 
                     Q4_1_1 = survey_median(Q4_1_1, na.rm = TRUE), 
                     Q4_1_2 = survey_median(Q4_1_2, na.rm = TRUE)),
    mapping = aes(Q4_1_1 / 100, Q4_1_2 / 100), 
    alpha = 0.5,
    color = "#ec008b"
  ) +  
  scale_x_continuous(breaks = seq(0, 1, 0.1), labels = scales::percent_format(accuracy = 1)) +
  scale_y_continuous(breaks = seq(0, 1, 0.1), labels = scales::percent_format(accuracy = 1)) +
  scatter_grid() +
  coord_equal() +
  labs(
    title = "What is the largest percentage of significance mismatch you would\naccept before...",
    subtitle = "Median responses in magenta",
    x = "sacrificing access to the administrative data",
    y = "adversely responding to a journal submission",
    caption = paste(missing_q4.1, "respondents did not answer")
  )

```

### Question 2

What is the largest percentage of sign mismatch you would accept before...?

*This is more conservative than significance, which seems good.*

```{r}
aea_weighted %>%
  group_by(is.na(Q4_2_1)) %>%
  summarize(n())

aea_weighted %>%
  group_by(is.na(Q4_2_2)) %>%
  summarize(n())

probs <- c(0, 0.05, 0.25, 0.5, 0.75, 0.95, 1)

aea_weighted %>%
  summarize(
    sign_mismatch = survey_quantile(Q4_2_1, quantile = probs, na.rm = TRUE)
  )

aea_weighted %>%
  summarize(
    sign_mismatch = survey_quantile(Q4_2_2, quantile = probs, na.rm = TRUE)
  )

```

```{r q4.2}
missing_q4.2 <- sum(is.na(pull(aea_weighted, Q4_2_1)) | is.na(pull(aea_weighted, Q4_2_2)))

ggplot() +
  geom_point(
    data = aea_weighted$variables,
    mapping = aes(Q4_2_1 / 100, Q4_2_2 / 100), 
    alpha = 0.05
  ) +
  geom_point(
    data = summarize(
      aea_weighted, 
      Q4_2_1 = survey_median(Q4_2_1, na.rm = TRUE), 
      Q4_2_2 = survey_median(Q4_2_2, na.rm = TRUE)
    ),
    mapping = aes(Q4_2_1 / 100, Q4_2_2 / 100), 
    alpha = 0.5,
    color = "#ec008b"
  ) +  
  scale_x_continuous(breaks = seq(0, 1, 0.1), labels = scales::percent_format(accuracy = 1)) +
  scale_y_continuous(breaks = seq(0, 1, 0.1), labels = scales::percent_format(accuracy = 1)) +  
  scatter_grid() +
  coord_equal() +
  labs(
    title = "What is the largest percentage of sign mismatch you would accept\nbefore...",
    subtitle = "Median responses in magenta",    
    x = "sacrificing access to the administrative data",
    y = "adversely responding to a journal submission",
    caption = paste(missing_q4.2, "respondents did not answer")
  )

```

### Question 3

What is the highest amount of absolute relative bias you would accept in an estimate before...?

```{r}
aea_weighted %>%
  group_by(is.na(Q4_3_1)) %>%
  summarize(n())

aea_weighted %>%
  group_by(is.na(Q4_3_2)) %>%
  summarize(n())

probs <- c(0, 0.05, 0.25, 0.5, 0.75, 0.95, 1)

aea_weighted %>%
  summarize(
    abs_relative_error = survey_quantile(Q4_3_1, quantiles = probs, na.rm = TRUE)
  )

aea_weighted %>%
  summarize(
    abs_relative_error = survey_quantile(Q4_3_2, quantiles = probs, na.rm = TRUE)
  )

```

```{r q4.3}
missing_q4.3 <- sum(is.na(pull(aea_weighted, Q4_3_1)) | is.na(pull(aea_weighted, Q4_3_2)))

ggplot() +
  geom_point(
    data = aea_weighted$variables,
    mapping = aes(Q4_3_1 / 100, Q4_3_2 / 100), 
    alpha = 0.05
  ) +
  geom_point(
    data = summarize(
      aea_weighted, 
      Q4_3_1 = survey_median(Q4_3_1, na.rm = TRUE), 
      Q4_3_2 = survey_median(Q4_3_2, na.rm = TRUE)
    ),
    mapping = aes(Q4_3_1 / 100, Q4_3_2 / 100), 
    alpha = 0.5,
    color = "#ec008b"
  ) +  
  scale_x_continuous(
    breaks = seq(0, 1.6, 0.2), 
    expand = expansion(mult = c(0, 0.15)), 
    labels = scales::percent_format(accuracy = 1)
  ) +
  scale_y_continuous(
    breaks = seq(0, 1.6, 0.2), 
    expand = expansion(mult = c(0, 0.15)), 
    labels = scales::percent_format(accuracy = 1)
  ) +  
  scatter_grid() +
  coord_equal() +
  labs(
    title = "What is the highest amount of absolute relative bias you would\naccept in an estimate before...",
    subtitle = "Median responses in magenta",    
    x = "sacrificing access to the administrative data",
    y = "adversely responding to a journal submission",
    caption = paste(missing_q4.3, "respondents did not answer")
  )

```

### Question 4

What is the largest confidence interval ratio you would accept in an estimate before...?

```{r}
aea_weighted %>%
  group_by(is.na(Q4_4_1)) %>%
  summarize(n())

aea_weighted %>%
  group_by(is.na(Q4_4_2)) %>%
  summarize(n())

probs <- c(0, 0.05, 0.25, 0.5, 0.75, 0.95, 1)

aea_weighted %>%
  summarize(
    ci_ratio = survey_quantile(Q4_4_1, quantiles = probs, na.rm = TRUE)
  )

aea_weighted %>%
  summarize(
    ci_ratio = survey_quantile(Q4_4_2, quantiles = probs, na.rm = TRUE)
  )

```

```{r q4.4}
missing_q4.4 <- sum(is.na(pull(aea_weighted, Q4_4_1)) | is.na(pull(aea_weighted, Q4_4_2)))

ggplot() +
  geom_point(
    data = aea_weighted$variables,
    mapping = aes(Q4_4_1, Q4_4_2), 
    alpha = 0.05
  ) +
  geom_point(
    data = summarize(
      aea_weighted, 
      Q4_4_1 = survey_median(Q4_4_1, na.rm = TRUE), 
      Q4_4_2 = survey_median(Q4_4_2, na.rm = TRUE)
    ),
    mapping = aes(Q4_4_1, Q4_4_2), 
    alpha = 0.5,
    color = "#ec008b"
  ) +  
  scale_x_continuous(limits = c(0, 10)) +
  scale_y_continuous(limits = c(0, 10)) +
  scatter_grid() +
  coord_equal() +
  labs(
    title = "What is the largest confidence interval ratio you would accept in\nan estimate before",
    subtitle = "Median responses in magenta",    
    x = "sacrificing access to the administrative data",
    y = "adversely responding to a journal submission",
    caption = paste(missing_q4.4, "respondents did not answer")
  )

```

## Section 5

### Question 1

5.1: Suppose you gain access to administrative data for regression analysis, but your access is constrained by a privacy budget. How would you spend your privacy budget from the following choices?

```{r q5.1}
missing_q5.1 <- sum(is.na(pull(aea_weighted, Q5_1)))

aea_weighted %>%
  filter(!is.na(Q5_1)) %>%  
  group_by(Q5_1) %>%
  summarize(n(), survey_prop(vartype = "ci")) %>%
  mutate(Q5_1 = fct_recode(
    Q5_1,
    `One regression specification with moderate noise\nand five robustness checks with more noise` =
      "One regression specification with moderate noise and five robustness checks with more   noise")
  ) %>%  
  mutate(Q5_1 = fct_rev(Q5_1)) %>%
  ggplot(aes(coef, Q5_1)) +
  geom_col() +
  geom_text(aes(label = label_percent(accuracy = 0.1)(coef)), hjust = -0.2) +
  scale_x_continuous(
    labels = scales::percent,
    expand = expansion(mult = c(0, 0.2))
  ) +
  labs(
    title = "Economists Want the Goldilocks Budget",
    subtitle = "Text: Suppose you gain access to administrative data for regression analysis, but your access is constrained by a\nprivacy budget. How would you spend your privacy budget from the following choices?",
    x = NULL,
    y = NULL,
    caption = paste(missing_q5.1, "respondents did not answer")
  ) +
  theme(panel.grid = element_blank())

```

## Software

```{r}
sessionInfo()

```